### 2017-07-06 Bright_Stars/LaTeX/preprint.tex

% WATERMARKS
\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{3}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Research Synergy and Drug Development: Bright Stars in Neighboring Constellations} % Please use "title case" (capitalize all terms in the title except conjunctions, prepositions, and articles).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Samet Keserci\textsuperscript{1},
%Samet Keserci\textsuperscript{1,2\Yinyang},
Eric Livingston\textsuperscript{2},
Lingtian Wan\textsuperscript{1,\textcurrency},
Alexander R. Pico\textsuperscript{3},
%Name5 Surname\textsuperscript{2\ddag},
%Name6 Surname\textsuperscript{2\ddag},
 \& George Chacko\textsuperscript{1*}
%with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} NETE Labs, NET ESolutions Corporation, McLean, VA, USA
\\
\textbf{2} Research Intelligence, Elsevier Inc., New York, NY, USA
\\
\textbf{3} Gladstone Institutes, San Francisco, CA, USA
\\
\bigskip

@@

Drug discovery and subsequent availability of a new breakthrough therapeutic or `cure' is a compelling example of societal benefit from research advances. These advances are invariably collaborative, involving the contributions of many scientists to a discovery network in which theory and experiment are built upon. To understand such scientific advances, data mining of public and commercial data sources coupled with network analysis can be used as a digital methodology to assemble and analyze component events in the history of a therapeutic. This methodology is extensible beyond the history of therapeutics and its use more generally supports (i) efficiency in  exploring  the scientific history of a research advance (ii) documenting and understanding collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.  As a proof of principle, we have conducted a case study of five anti-cancer therapeutics. We have linked the work of over 235,000 authors in roughly 103,000 scientific publications that capture the research crucial for the development of these five therapeutics. We have enriched the content of networks of these therapeutics by annotating them with information on research awards as well as peer review that preceded these awards. Applying retrospective citation discovery, we have identified a core set of publications cited in the networks of all five therapeutics and additional intersections in combinations of networks as well as awards from the National Institutes of Health that supported this research. Lastly, we have mapped these awards to their cognate peer review panels, identifying another layer of collaborative scientific activity that influenced the research represented in these networks.

\linenumbers

@@

\section*{Materials and Methods}  A set of five anti-cancer therapeutics, three drugs and two biologicals, approved for use in humans by the Food and Drug Administration was selected for this study (Table 1). Imatinib~\cite{bibImatinib} and Sunitinib~\cite{bibSunitinib} are tyrosine kinase inhibitors, Nelarabine~\cite{bibNelarabine} is a nucleoside analog, and Ramucirumab~\cite{bibRamucirumab} and Alemtuzumab (Campath)~\cite{bibAlemtuzumab} are humanized antibodies that target the CD52 and vEGFR-2 cell surface receptors respectively. For each of these therapeutics, a set of relevant scientific publications was constructed as in Williams et al.~\cite{bibWilliams} but with specific modifications detailed below. An allowance of 2 months was also made for `publication lag' when assembling referenced material. For example, if a therapeutic was approved on Jan 1, 2017, documents published  on or before March 31, 2017 were included. For each of the five therapeutics, a first-generation list of PubMed identifiers (citing\_pmid) was harvested from the five different data sources (below). \textbf{[Insert Table 1]}

@@

\textbf{PubMed and Scopus} Citing\_pmids from the five different sources above  were combined and deduplicated. Using the Scopus database and its APIs. The manually-generated list of pmids taken from the five sources mentioned (Clinical Trials, FDA Documents, Patents, Post-Approval Literature, and Pre-Approval Literature Searches) were searched in Scopus, using the basic Scopus Search API, to arrive at a list of Scopus IDs (citing\_sid) for the publications. The Scopus Abstract Retrieval API was then used to retrieve a more comprehensive record for each of the SIDs comprising that list of publications Next, for each of these publication records citing\_sid), we used the Scopus Author Retrieval API to retrieve a full record for each unique author in the  publication set. We also used the Abstract Retrieval API to collect records for each of the publications cited by the first generation of publications. This set of cited publications is the cited\_sid set.  Using the same Author Retrieval API, we then gathered data for each of the unique authors affiliated with the cited\_sid publications. Completion of the process yields two sets of publications, citing\_sid and cited\_sid, with citation links between them and full information on all authors for both generations. Finally, for each author in the study, we used the standard Scopus Search API once more to retrieve a smaller record for every publication affiliated with them in Scopus, in order to tally their overall publication output. While author records in Scopus have overall publication counts as part of the record, by manually downloading each of them, we can store and count them by type (i.e. article, book chapter, Editorial, review, etc.). This allowed us to more precisely arrive at publication totals for only those publication types that are relevant for this study. [which are]

Whereas mapping between PubMed and Scopus identifiers at the citing\_pmid and citing\_sid stage resulted in 1\% or less information loss, mapping at the cited\_sid to cited\_pmid resulted in a loss of roughly 15-20 \% of target records. Accordingly the Scopus data  was used as the backbone of the publication component of the network and the cited\_pmid information was treated as an annotation layer.  These observations are summarized in Table 2. \textbf{[Insert Table 2]}

@@

\textbf{Networks} The resultant data were modeled as networks and analyzed using metrics based on network topology. We calculated the propagated in-degree rank (PIR) and ratio of basic rankings (RBR) metrics of Williams ~~\cite{bibWilliams}. PIR represents the sum of aggregated citation scores (first and second degree only)  for all articles in a network that can be attributed to an author. In addition to computing PIR for all authors in each network, we also combined the citation data for all five networks and computed a networkPIR (nPIR) score, which was also normalized to the sum of individual PIR scores within each network as the PIRpartitionRatio (PPR) as a way to measure inter-network influence. RBR is intended to represent the fraction of a researcher's output that is in a network and is defined as the ratio of the number of publications in network to the number of publications in a background dataset for an author. In its original specification, the background dataset for RBR was constructed by keyword searches of PubMed. A potential weakness of this keyword based approach is that keywords do not effectively capture the field or the total output of an author even if multiple background samples are taken. Therefore, we created two new variants of the RBR; network RBR (nRBR) and global-based RBR (gRBR). nRBR uses all publications in our set of five therapeutics as background and dRBR takes advantage of the Scopus author\_id to capture the total article output of an author as background. Thus, nRBR and dRBR normalize a researcher's in-network contributions to backgrounds based on total network and total researcher productivity respectively. The details of how these metrics were calculated are provided in supplementary material \nameref{S1_File}.\\

@@

\section*{Results and Discussion} 
\textbf{Publications} Scientific publications form the backbone of each of these five networks. Our initial assumptions of appropriate citation and retrospective citation discovery (Introduction) suggest that network nodes that are common to multiple networks are likely to be influential. We calculated intersection counts for all possible combinations of publications in the Alemtuzumab, Imatinib, Nelarabine, Ramucirumab, and Sunitinib networks (\nameref{S2_Table 1}). We also applied intersection analysis at a finer level of granularity by computing intersection counts for both first generation citations (citing\_pmid) and second generation citations (cited\_sid). The results are displayed as Venn diagrams in Fig. 1. \textbf{[Insert Fig. 1]}

@@

The intersection of all five networks consists of 14 publications out of a total of 91,991 unique Scopus identifiers. Strikingly, not even a single publication is common to all five networks at the first generation level (citing\_sid) although a single publication, the pathbreaking work of Kohler and Milstein on the production of monoclonal antibodies~\cite{bibKohler}, is cited in four out of five networks. All 14 publications are in the second generation of citations (cited\_sid) and another 198 comprise the sum of intersections in all possible four-network combinations, roughly an order of magnitude greater than the case of cited references. We manually grouped these 14 publications using high level descriptive terms and observed that this group was composed of  statistical methods (5 publications), molecular and cell biological methods (4 publications), analytical and structural biology techniques (3 publications) and cancer biology (2 publications). Of these last two, one is a review of the p53 gene~\cite{bibLevine} and the second is a study of angiogenesis in children with acute lymphoblastic leukemia~\cite{bibFolkman}. Thus, the majority of this small set of 14 publications describes methods that are heavily cited in these therapeutic development networks, which is consistent with observations of the general scientific literature ~\cite{bibVanNoorden}. The relationship between core publications and their therapeutic networks is visualized in Fig. 2. As the subject of another study, we are actively working on a scalable automated strategy to characterize the entire dataset as well as all combinations of intersections between networks using high level descriptive terms.  \textbf{[Insert Fig. 2]}.

\begin{figure}[!h]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{1.3}{
\includegraphics[scale=0.1]{cy_core14_v2csv_5b.png}}
\caption{{\bf Core Publications in Networks}  The outer ring of blue nodes identifies first generation publications (citing\_sid) for each therapeutic. Nodes in the inner ring are sized by a gradient proportion to total degree count with an upper limit of 30 and are colored by a gradient proportional to the number of drug connections (2 to 5). 14  publications are common to all five networks (Table 3) and are colored red. The remaining nodes in the inner ring connect to between 2 and 4 drugs each and are labeled accordingly. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
\label{fig2}
\end{adjustwidth}
\end{figure}

@@

\textbf{Network Metrics} To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information). The nPIR metric describes the sum of aggregated citation scores for all articles that a researcher has in all five networks. The PIRpartitionRatio (PPR) results from normalizing nPIR to the sum of individual PIR scores to gain insight into holo-network influence. A limitation of the nPIR and nRBR measurements is that they are valid only for the network(s) being studied. Scaling from five to the more than 1400 drugs approved by the FDA (and their many variants) would address this limitation~\cite{bibKinch} although other data related issues may well emerge.

While theoretically appealing (Materials and Methods), the gRBR is the most sensitive to data quality since it relies on an accurate estimate of total productivity of a researcher, which is sensitive to data quality in bibliometric databases. We found several instances in the top 10\% of PIR scores where the gRBR was implausible likely on account of polysemy, synonymy, or incompleteness. This metric is therefore likely to be useful when the author disambiguation problem and article capture is resolved to the point where data quality is significantly improved and is not recommended except when strong confidence exists in the total productivity counts. These metrics may be best used in conjunction with positional measures such as quantiles to define populations of researchers within related networks, e.g, the top 25 researchers based on nPIR scores of all researchers in our dataset (\nameref{S3_Table 2}). These `bright stars in neighboring constellations', represent elite performers in network(s) of clinical and basic science expertise again reinforcing the concept of collaborative translational achievements built upon a body of basic science. Beyond simple aggregation, weighting, and normalization that we have used, a variety of citation metrics such as SNIP~\cite{bibWaltman}, with different normalization strategies at the field, journal, and article level are available for impact analysis and these could be applied to such networks depending on the features of these networks and the aim of the study~\cite{bibIoannidis}. The use of these citation measures will assume greater importance when scale up from small numbers of networks to a greater proportion of the global network.

@@

\paragraph*{S3 Table 2}
\label{S3_Table 2}
{\bf Elite Performers in Networks}

\section*{Acknowledgments}  This study would not have been possible without data that is made publicly available by NIH and the FDA. We thank Tandy Warnow for critical comments and advice on formalizing definitions. We thank Sandeep Somaiya from NETE and Holly J. Falk-Krzesinski from Elsevier for their support of this project.

\nolinenumbers

@@

\end{thebibliography}
\end{document}

>>>>

% WATERMARKS
%\usepackage{draftwatermark}
%\SetWatermarkText{Preprint}
%\SetWatermarkScale{3}

@@

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Research Synergy and Drug Development: Bright Stars in Neighboring Constellations} % Please use "title case" (capitalize all terms in the title except conjunctions, prepositions, and articles).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Samet Keserci\textsuperscript{1},
%Samet Keserci\textsuperscript{1,2\Yinyang},
Eric B. Livingston\textsuperscript{2},
Lingtian Wan\textsuperscript{1,\textcurrency},
Alexander R. Pico\textsuperscript{3},
%Name5 Surname\textsuperscript{2\ddag},
%Name6 Surname\textsuperscript{2\ddag},
 \& George Chacko\textsuperscript{1*}
%with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} NETE Labs, NET ESolutions Corporation, McLean, VA, USA
\\
\textbf{2} Research Intelligence, Elsevier Inc., New York, NY, USA
\\
\textbf{3} Gladstone Institutes, San Francisco, CA, USA
\\
\bigskip

@@

Drug discovery and subsequent availability of a new breakthrough therapeutic or `cure' is a compelling example of societal benefit from research advances. These advances are invariably collaborative, involving the contributions of many scientists to a discovery network in which theory and experiment are built upon. To understand such scientific advances, data mining of public and commercial data sources coupled with network analysis can be used as a digital methodology to assemble and analyze component events in the history of a therapeutic. This methodology is extensible beyond the history of therapeutics and its use more generally supports (i) efficiency in  exploring  the scientific history of a research advance (ii) documenting and understanding collaboration (iii) portfolio analysis, planning and optimization (iv) communication of the societal value of research.  As a proof of principle, we have conducted a case study of five anti-cancer therapeutics. We have linked the work of roughly 237,000 authors in 106,000 scientific publications that capture the research crucial for the development of these five therapeutics. We have enriched the content of networks of these therapeutics by annotating them with information on research awards as well as peer review that preceded these awards. Applying retrospective citation discovery, we have identified a core set of publications cited in the networks of all five therapeutics and additional intersections in combinations of networks as well as awards from the National Institutes of Health that supported this research. Lastly, we have mapped these awards to their cognate peer review panels, identifying another layer of collaborative scientific activity that influenced the research represented in these networks.

%\linenumbers

@@

\section*{Materials and Methods}  A set of five anti-cancer therapeutics, three drugs and two biologicals, approved for use in humans by the Food and Drug Administration (FDA) was selected for this study (Table 1). Imatinib~\cite{bibImatinib} and Sunitinib~\cite{bibSunitinib} are tyrosine kinase inhibitors, Nelarabine~\cite{bibNelarabine} is a nucleoside analog, and Ramucirumab~\cite{bibRamucirumab} and Alemtuzumab (Campath)~\cite{bibAlemtuzumab} are humanized antibodies that target the CD52 and vEGFR-2 cell surface receptors respectively. For each of these therapeutics, a set of relevant scientific publications was constructed as in Williams et al.~\cite{bibWilliams} but with specific modifications detailed below. An allowance of 2 months was also made for `publication lag' when assembling referenced material. For example, if a therapeutic was approved on Jan 1, 2017, documents published  on or before March 31, 2017 were included. For each of the five therapeutics, a first-generation list of PubMed identifiers (citing\_pmid) was harvested from the five different data sources (Table 1).

@@

\textbf{PubMed and Scopus} Citing\_pmids from the five different sources above  were combined and deduplicated. Using the Scopus database and its APIs. The manually-generated list of pmids taken from the five sources mentioned (Clinical Trials, FDA Documents, Patents, Post-Approval Literature, and Pre-Approval Literature Searches) were searched in Scopus, using the basic Scopus Search API, to arrive at a list of Scopus IDs (citing\_sid) for the publications. The Scopus Abstract Retrieval API was then used to retrieve a more comprehensive record for each of the SIDs comprising that list of publications Next, for each of these publication records citing\_sid), we used the Scopus Author Retrieval API to retrieve a full record for each unique author in the  publication set. We also used the Abstract Retrieval API to collect records for each of the publications cited by the first generation of publications. This set of cited publications is the cited\_sid set.  Using the same Author Retrieval API, we then gathered data for each of the unique authors affiliated with the cited\_sid publications. Completion of the process yields two sets of publications, citing\_sid and cited\_sid, with citation links between them and full information on all authors for both generations. Finally, for each author in the study, we used the standard Scopus Search API once more to retrieve a smaller record for every publication affiliated with them in Scopus, in order to tally their overall publication output. While author records in Scopus have overall publication counts as part of the record, by manually downloading each of them, we can store and count them by type (i.e. article, book chapter, Editorial, review, etc.). This allowed us to more precisely arrive at publication totals for only those publication types that are relevant for this study.

Whereas mapping between PubMed and Scopus identifiers at the citing\_pmid and citing\_sid stage resulted in 1\% or less information loss, mapping at the cited\_sid to cited\_pmid resulted in a loss of roughly 15-20 \% of target records. Accordingly the Scopus data  was used as the backbone of the publication component of the network and the cited\_pmid information was treated as an annotation layer.  These observations are summarized in Table 2.

@@

\textbf{Networks} The resultant data were modeled as networks and analyzed using metrics based on network topology. We calculated the propagated in-degree rank (PIR) and ratio of basic rankings (RBR) metrics of Williams ~~\cite{bibWilliams}. PIR represents the sum of aggregated citation scores (first and second degree only)  for all articles in a network that can be attributed to an author. In addition to computing PIR for all authors in each network, we also combined the citation data for all five networks and computed a networkPIR (nPIR) score, which was also normalized to the sum of individual PIR scores within each network as the PIRpartitionRatio (PPR) as a way to measure inter-network influence. RBR is intended to represent the fraction of a researcher's output that is in a network and is defined as the ratio of the number of publications in network to the number of publications in a background dataset for an author. In its original specification, the background dataset for RBR was constructed by keyword searches of PubMed. A potential weakness of this keyword based approach is that keywords do not effectively capture the field or the total output of an author even if multiple background samples are taken. Therefore, we created two new variants of the RBR; network RBR (nRBR) and global-based RBR (gRBR). nRBR uses all publications in our set of five therapeutics as background and gRBR takes advantage of the Scopus author\_id to capture the total article output of an author as background. Thus, nRBR and gRBR normalize a researcher's in-network contributions to backgrounds based on total network and total researcher productivity respectively. The details of how these metrics were calculated are provided in supplementary material \nameref{S1_File}.\\

@@

\section*{Results and Discussion} 
\textbf{Publications} Scientific publications form the backbone of each of these five networks. Our initial assumptions of appropriate citation and retrospective citation discovery (Introduction) suggest that network nodes that are common to multiple networks are likely to be influential. We calculated intersection counts for all possible combinations of publications in the Alemtuzumab, Imatinib, Nelarabine, Ramucirumab, and Sunitinib networks (\nameref{S2_Table 1}). We also applied intersection analysis at a finer level of granularity by computing intersection counts for both first generation citations (citing\_pmid) and second generation citations (cited\_sid). The results are displayed as Venn diagrams in Fig. 1.

@@

The intersection of all five networks consists of 14 publications out of a total of 106,720 unique Scopus identifiers (Supplemental Data, Table 1). Strikingly, not even a single publication is common to all five networks at the first generation level (citing\_sid) although a single publication, the pathbreaking work of Kohler and Milstein on the production of monoclonal antibodies~\cite{bibKohler}, is cited in four out of five networks. All 14 publications are in the second generation of citations (cited\_sid) and another 198 comprise the sum of intersections in all possible four-network combinations, roughly an order of magnitude greater than the case of cited references. We manually grouped these 14 publications using high level descriptive terms and observed that this group was composed of  statistical methods (5 publications), molecular and cell biological methods (4 publications), analytical and structural biology techniques (3 publications) and cancer biology (2 publications). Of these last two, one is a review of the p53 gene~\cite{bibLevine} and the second is a study of angiogenesis in children with acute lymphoblastic leukemia~\cite{bibFolkman}. Thus, the majority of this small set of 14 publications describes methods that are heavily cited in these therapeutic development networks, which is consistent with observations of the general scientific literature ~\cite{bibVanNoorden}. The relationship between core publications and their therapeutic networks is visualized in Fig. 2. As the subject of another study, we are actively working on a scalable automated strategy to characterize the entire dataset as well as all combinations of intersections between networks using high level descriptive terms.

\begin{figure}[!h]
\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{1.3}{
\includegraphics[scale=0.1]{cy_core14_v2csv_5b.png}}
\caption{{\bf Core Publications in Networks}  The arcs of blue nodes identify first generation publications (citing\_sid) for each therapeutic. Nodes in the inner ring are sized by a gradient proportion to total degree count with an upper limit of 30 and are colored by a gradient proportional to the number of drug connections (2 to 5). 14  publications are common to all five networks (Table 3) and are colored red. The remaining nodes in the inner ring connect to between 2 and 4 drugs each and are labeled accordingly. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
\label{fig2}
\end{adjustwidth}
\end{figure}

@@

\textbf{Network Metrics} To quantify network data and to identify influential researchers in and across networks, we calculated PIR and RBR scores for all researchers as well as nPIR, PPR, nRBR, and gRBR scores (Materials and Methods, Supplemental Information, Table 2). The nPIR metric describes the sum of aggregated citation scores for all articles that a researcher has in all five networks. The PIRpartitionRatio (PPR) results from normalizing nPIR to the sum of individual PIR scores to gain insight into holo-network influence. A limitation of the nPIR and nRBR measurements is that they are valid only for the network(s) being studied. Scaling from five to the more than 1400 drugs approved by the FDA (and their many variants) would address this limitation~\cite{bibKinch} although other data related issues may well emerge.

While theoretically appealing (Materials and Methods), the gRBR is the most sensitive to data quality since it relies on an accurate estimate of total productivity of a researcher, which is sensitive to data quality in bibliometric databases. For example, we found several instances in the top 10\% of PIR scores where the gRBR was implausible likely on account of polysemy, synonymy, or incompleteness. This metric is therefore likely to be useful when the author disambiguation problem and article capture is resolved to the point where data quality is significantly improved and is not recommended except when strong confidence exists in the total productivity counts. These metrics may be best used in conjunction with positional measures such as quantiles to define populations of researchers within related networks, e.g, the top 25 researchers based on nPIR scores of all researchers in our dataset (\nameref{S3_Table 2}). These `bright stars in neighboring constellations', represent elite performers in network(s) of clinical and basic science expertise again reinforcing the concept of collaborative translational achievements built upon a body of basic science. Beyond simple aggregation, weighting, and normalization that we have used, a variety of citation metrics such as SNIP~\cite{bibWaltman}, with different normalization strategies at the field, journal, and article level are available for impact analysis and these could be applied to such networks depending on the features of these networks and the aim of the study~\cite{bibIoannidis}. The use of these citation measures will assume greater importance when scale up from small numbers of networks to a greater proportion of the global network.

@@

\section*{Acknowledgments}  This study would not have been possible without data that is made publicly available by NIH and the FDA. We thank Tandy Warnow for critical comments and advice on formalizing definitions. We thank Sydney Gomes and Caitlin Werle for assistance with graphics. We thank Sandeep Somaiya from NETE as well as Daniel Calto and Holly J. Falk-Krzesinski from Elsevier for their support of this project.

%\nolinenumbers

@@

\end{thebibliography}

\paragraph*{S3 Table 2}
\label{S3_Table 2}
{\bf Elite Performers in Networks} 
\end{document}

### 2017-07-06 Bright_Stars/Submission/biorxiv_supp.tex

@@

Next we define the nPIR score  of author $\mathfrak{a}$ within network $\mathcal{N}$ (denoted by $nPIR\mathfrak{a}$) to  be  $pir_{\mathcal{N}}(\mathfrak{a})$; in other words
it is the $pir$ score based on the network $\mathcal{N}$.

%$npir(\mathfrak{a})$, which is $pir$ score based on the  total network $\mathcal{N}$.

% For convenience, instead of denoting it $pir_N$, we use $npir$   Furthermore

We define the PIR partition ratio (PPR)  of author $\mathfrak{a}$ (denoted by $ppr(\mathfrak{a})$)
to be 
%:\mathcal{A}\rightarrow [0,\infty]$  of author $\mathfrak{a}$ as 
$$ppr(\mathfrak{a})= \dfrac{ nPIR({\mathfrak{a}})} {\sum_{i=1}^{5} pir_{N_i}(\mathfrak{a})} $$
%where $\mathcal{A}$ is the set of authors in $\mathcal{N}$  and  $pir_{N_i}(\mathfrak{a})$.
% is the PIR score of the author $\mathfrak{a}$ in $\mathcal{N}_i$.
%restricted to only drug network $\mathcal{D}_i$ .

There are cases where PPR can be greater than 1.
% and one way this can occur is when an author's influence extends beyond $\mathcal{N}_i$ but within $\mathcal{N}$.

\vspace{.1in}

\paragraph{\textbf {Ratio of Basic Rankings (RBR)}}
\begin{itemize}
\item nRBR (i.e., network RBR) is the ratio of an author's publication count in a given network $\mathfrak{n}$ to the total publication count for that author  in $\mathcal{N}$.
 Thus, nRBR depends on both the author $\mathfrak{a}$ and the given network $\mathfrak{n}$, and is denoted by $nRBR(\mathfrak{a},\mathfrak{n})$.
%We define in-degree count $ic_{d_i}(\mathfrak{a})$ of an author $\mathfrak{a}$ as the total number of the publication which is in the network $\mathcal{N}_i$ of the drug $d_i$, similarly lets $ic_{n}$ be the number of the paper that author $\mathfrak{a}$ published in the total Network(5-drug's network) $\mathcal{N}$. Then we define, nRBR of an author $\mathfrak{a}$  for a drug $d_i$ as follow.
%$$ nrbr_{d_i}(\mathfrak{a}) = \dfrac{ic_{d_i}(\mathfrak{a})}{ic_{N}(\mathfrak{a})}$$
\item gRBR, or global RBR, is the ratio of an author's count of publications in network $\mathfrak{n}$ to the author's total publication count in the global network $\mathcal{G}$,
and is denoted by gRBR$(\mathfrak{a},\mathfrak{n})$. 
%Thus, the $grlobRBR(\mathfrak{a},n)$ score of an author  $\mathfrak{a}$  for the drug $d_i$ is defined as 
%$$grbr_{d_i}(\mathfrak{a}) = \dfrac{ic_{d_i}(\mathfrak{a})}{ic_{G}(\mathfrak{a})}$$
%where $ic_{G}$ is the total number of publication that an author $\mathfrak{a}$ currently has.
\end{itemize}
\noindent
nRBR$(\mathfrak{a},n)$ and gRBR$(\mathfrak{a},n)$ are both ratios with the same numerator but with different denominators, and  
$0 \leq$ nRBR$(\mathfrak{a},\mathfrak{n}) \leq$ gRBR$(\mathfrak{a},\mathfrak{n}) \leq 1$.

\end{document}
 Here in this study we focus on the $ppr$ values which is greated than 1. Greater the value, the higher the level of interactions(citation edges/flow) of the author's publication between other publications in the subnetworks. We have proved in Proposition 0.1 that a lower bound for ppr score of an author is 0.2. The cases where $ppr\leq1$  will be addressed in the next study due the coupling of intersection count and inter-citation issues.

\begin{proposition}
Let the set $\mathcal{K}$ be the union of $k\geq 2$ subnetworks, and N be the complete citation network of the set K. Then the lower bound for the $ppr$ score is 1/k. 
\end{proposition}

\begin{proof} Let $\mathcal{A}_\mathfrak{a}^N$ be the set publications $\{\mathfrak{p}_1,\mathfrak{p}_2,...,\mathfrak{p}_m\} $  written by an author $\mathfrak{a}$ in the whole network $\mathcal{N}$. For any $\mathfrak{p}_j \in \mathcal{A}_\mathfrak{a}^N$, lets define sequence of publication $S_r^n (\mathfrak{p}_j)$ be the sequence of publication(with duplicates) having exactly $r$ number of edges  apart in the directed graph of citation Network. Then, aggragated citation of a paper  $\mathfrak{p}_j$ in any network $\mathfrak{n}$ can also be written
$$wc_n(\mathfrak{p}_j) = |S_1^n(\mathfrak{p}_j)| + |S_2^n(\mathfrak{p}_j)|$$ 
where $|\cdot|$ defined as the length of the sequence. Since for any subnetwork $d_i$, $|S_r^{d_i}| \leq  |S_r^N| $
for $r \geq1$, we have then,

\begin{equation}
\begin{split}
\sum_{i=1}^k wc_{d_i}(\mathfrak{p}_j) &= \sum_{i=1}^k |S_1^{d_i}(\mathfrak{p}_j)| + |S_2^{d_i}(\mathfrak{p}_j)| \\
 &\leq \sum_{i=1}^k |S_1^{N}(\mathfrak{p}_j)| + |S_2^{N}(\mathfrak{p}_j)| \\
 &=k(|S_1^{N}(\mathfrak{p}_j)| + |S_2^{N}(\mathfrak{p}_j)|)\\
 &=k(wc_N(\mathfrak{p}_j))
\end{split}
\end{equation}

Next  using  inequality (1) and changing the order of sums due to finite index sum gives,

\begin{equation}
\begin{split}
\sum_{i=1}^k pir_{d_i}(\mathfrak{a})&=\sum_{i=1}^k \sum_{j=1}^m wc_{d_i}(\mathfrak{p}_j)=\sum_{j=1}^m \sum_{i=1}^k wc_{d_i}(\mathfrak{p}_j) \\
&\leq k\sum_{j=1}^m  wc_N(\mathfrak{p}_j) = k (npir(\mathfrak{a}))
\end{split}
\end{equation}

which implies that \\

\begin{equation}
\begin{split}
\dfrac{1}{k}\leq \dfrac{npir(\mathfrak{a})}{\sum_{i=1}^k pir_{d_i}(\mathfrak{a})}=ppr(\mathfrak{a})
\end{split}
\end{equation}
\end{proof}
\clearpage

>>>>

\usepackage{changepage}
\usepackage{graphics}

@@

Next we define the nPIR score  of author $\mathfrak{a}$ within network $\mathcal{N}$ (denoted by $nPIR\mathfrak{(a)}$) to  be  $pir_{\mathcal{N}}(\mathfrak{a})$; in other words
it is the $pir$ score based on the network $\mathcal{N}$.

$$ppr(\mathfrak{a})= \dfrac{ nPIR({\mathfrak{a}})} {\sum_{i=1}^{5} pir_{N_i}(\mathfrak{a})} $$

There are cases where PPR can be greater than 1.

\vspace{0.05 in}
\paragraph{\textbf {Ratio of Basic Rankings (RBR)}}
\begin{itemize}
\item nRBR (i.e., network RBR) is the ratio of an author's publication count in a given network $\mathfrak{n}$ to the total publication count for that author  in $\mathcal{N}$.
 Thus, nRBR depends on both the author $\mathfrak{a}$ and the given network $\mathfrak{n}$, and is denoted by $nRBR(\mathfrak{a},\mathfrak{n})$.
\item gRBR, or global RBR, is the ratio of an author's count of publications in network $\mathfrak{n}$ to the author's total publication count in the global network $\mathcal{G}$,
and is denoted by gRBR$(\mathfrak{a},\mathfrak{n})$. 
\end{itemize}
\noindent
nRBR$(\mathfrak{a},n)$ and gRBR$(\mathfrak{a},n)$ are both ratios with the same numerator but with different denominators, and  
$0 \leq$ nRBR$(\mathfrak{a},\mathfrak{n}) \leq$ gRBR$(\mathfrak{a},\mathfrak{n}) \leq 1$.

\clearpage

\begin{table}[!ht]
\begin{adjustwidth}{-0.5 in}{0 in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{{\bf Intersection of Five Networks: Second Generation Publications}}
\scalebox{0.8}{\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
\hline
SourceYear & SourceName & Author(s) \\ 
  \hline
1958 & J. Am. Stat. Assoc. & Kaplan ER, Meier P. \\ 
1963 & Science & Jerne, NK and Nordin, AA.  \\ 
1972 & J R Stat Soc & Cox DR.  \\ 
1976 & Anal. Biochem. & Bradford MM. \\ 
1977 & Br J Cancer & R. Peto, M.C. Pike, and P. Armitage  \\ 
1977 & Proc. Natl. Acad. Sci. & Sanger FS., Nicklen S, Coulson AR.  \\ 
1983 & J Immunol Methods & Mosmann T.  \\ 
1984 & Adv Enzyme Regul & Chou TC, Talalay P.  \\ 
1989 & Molecular Cloning: A Laboratory Manual & Sambrook, J., Fritsch, E. and Maniatis, T.  \\ 
1994 & Acta Crystallogr D & Collaborative Computational Project 4 \\ 
1994 & Acta Crystallogr. A & Navaza J.  \\ 
1997 & Cell & Levine AJ. \\ 
1997 & Am. J. Pathol. & Perez-Atayde AR, Sallan SE, Tedrow U, Connors S, Allred E, Folkman J.  \\ 
1998 & CA: A Cancer Journal for Clinicians & Landis SH, Murray T,  Bolden S, Wingo PA. \\ 
\hline
\end{tabular}}
\vspace{2.5 mm}
\begin{flushleft}
Publications at the intersection of all five networks are listed above. All 14 publications are found in the second generation of references(cited\_sid, Fig 2 Right Panel). 
\end{flushleft}
\label{table3}
\end{adjustwidth}
\end{table}
\clearpage

\begin{table}[!ht]
\centering
\caption{
{\bf Elite Performers}}
\vspace{2.5 mm}
\begin{tabular}{|l| l| l|}
\hline
Name& nPIR & PPR \\
\hline
\hline
Ferrara N.	 & 46693 & 1.12 \\ 
Folkman J. & 23660 & 1.15 \\ 
Ullrich A. & 23034 & 1.46 \\ 
Jain R. & 15267 & 1.13 \\ 
Heldin C.	& 15148 & 1.21 \\ 
Druker B.	& 15088 & 1.16 \\ 
Schlessinger J.	& 14996 & 1.48 \\ 
Dvorak H.	 & 14230 & 1.13 \\ 
 Alitalo K.	& 13812 & 1.24 \\ 
 Slamon D. & 13587 & 1.46 \\ 
 Baselga J. & 12908 & 1.36 \\ 
 Kantarjian H. & 12029 & 1.17 \\ 
 Hicklin D.	 & 11775 & 1.17 \\ 
 Witte O. & 11449 & 1.08 \\ 
 Hanahan D. & 11072 & 1.19 \\ 
 Buchdunger E.	 & 11032 & 1.22 \\ 
 Risau W.	& 10950 & 1.24 \\ 
 Talpaz M.	 & 10713 & 1.13 \\ 
 Mendelsohn J.	 & 10534 & 1.54 \\ 
 Lydon N. & 9988 & 1.18 \\ 
 Goldman J. & 9927 & 1.11 \\ 
 Shibuya M. & 9639 & 1.21 \\ 
 Kitamura Y. & 9486 & 1.24 \\ 
 Waldmann H. & 9363 & 1.04 \\ 
 Kerbel R.	 & 9266 & 1.16 \\ 
  \hline
\end{tabular}
\vspace{2.5 mm}
\begin{flushleft} Researchers with the highest nPIR scores in the network of 5 anti-cancer therapeutics are listed. Also shown for each researcher is their PIRpartitionRatio (PPR). The nPIR indicates influence across all five networks and the PPR provides an estimate of how this influence is partitioned across each of the five networks (Materials and Methods). This list and its ordering should be considered in the context of the data being analyzed and not interpreted as an absolute ordering of research excellence in the field.
\end{flushleft}
\label{table2}
\end{table}
